HO unification from object language to meta language

### 2024-02-12 main.tex
Tex update

% Let upper-case letter unification variables and lower case variables defined
% constants of the object language. We take as example the following two
% unification problems in our \ol:

% \begin{center}
%   \coqIn{(fun x => P x) = P}
% \end{center}

% The first problem, if

% \begin{center}
%   \elpiIn{p (lam x\ (app F x)) :- ... F ...}
% \end{center}

% cannot unify with goals like

% \begin{center}
%   \elpiIn{p (lam x\ app (app (const "f") x) x).}
% \end{center}

% Since \elpiIn{F} does not see \elpiIn{x} even though it is applied to \elpiIn{x}
% in the object language.

>>>>

\section{Term compilation}

In order to present the the compilation of the \ol terms so that higher order
unification can be performed, we need a second and mor powerful representation
of the \ol terms so that variables have a scope. This specification is shown
in the code snippet below.

\begin{mintedTcolorbox}{elpi}
  kind ml.tm type.
  type ml.app list ml.tm -> ml.tm.
  type ml.lam (ml.tm -> ml.tm) -> ml.tm.
  type ml.c string -> ml.tm.
  type ml.uv  nat -> list ml.tm -> ml.tm.
\end{mintedTcolorbox}

\noindent In particular a \elpiIn{ml.uv} term is meant as a unification variable
of the meta-language. Therefore, the unification between \elpiIn{ml.lam x\
ml.lam y\ ml.uv 1 [x, y]} and \elpiIn{ml.lam x\ ml.lam y\ ml.uv 0 [x]} is
supposed to be unified by the internal unification procedure of the \ml (for
this example, the substitution for \elpiIn{uv 0} is \elpiIn{ml.lam x\ ml.lam y\
ml.uv 2 [x]} whereas the substitution for \elpiIn{uv 1} is \elpiIn{ml.lam x\
ml.uv 2 [x]}).

Moreover, if \elpiIn{ml.uv} stands for meta-variables, the \elpiIn{app} and the
\elpiIn{lam} constructors are the nodes for the terms of the \ol. Therefore, we
cannot claim that \elpiIn{ml.lam x\ ml.app [ml.c "f", x]} and \elpiIn{ml.c "f"}
unify, since, even though the first is the $\eta$-expansion of the second, the
\ml does not know how to $\eta\beta$-reduce the terms of the \ol.

The compilation phase is quite straightforward, each constructor of type
\elpiIn{tm} is mapped to its corresponding version of type \elpiIn{ml.tm}. A
slight different approach is taken in the case of terms of the form \elpiIn{app
[uv N | L]}, where the term is translated into \elpiIn{tm.un M L}, that is, a
new meta-variable \elpiIn{M} with scope \elpiIn{L}.

This latter term transformation is untying the original variable \elpiIn{N} of
the \ol from the compiled term in the \ml. This means that when \elpiIn{M} is
instantiated into the \ml, we need to transfer the substitution to the \ol. In
order to bridge instantiation of meta-variables with the \ol variables, an ad
hoc \texttt{link} is crafted between the two variables.
